A New Method of Modelling Tuneable Lasers with Functional Composition

### 2019-07-13 Thesis/Model/Model.tex
Fixed typo

\subsection{Dispersion}
Within the laser cavity, the dispersion is dominated by the \gls{cfbg}. In comparison, the dispersion due to the fibre is negligible. The dispersive terms of \eqref{eq:nlse} give
\begin{align}
\label{eq:dispde}
	\pdiff{A}{z} = -i \frac{\beta_2}{2} \pdiff[2]{A}{T},
\end{align}
and since dispersion acts in the frequency domain it is convenient to take the Fourier transform\footnote{We use $\displaystyle \FT{f} = (2 \pi)^{1/2} \int_\mathbb{R} f(x) \textrm{e}^{i \omega x} \df x$ as the definition of the Fourier transform.} of \eqref{eq:dispde} \cite{debnath, gradshteyn}, giving
\begin{align*}
	\pdiff{}{z}\FT{A} &= i\frac{\omega^2}{2}\beta_2 \FT{A}.
\end{align*}
The effect of dispersion is then given by the map
\begin{align*}
D(A) &= \FTi{\textrm{e}^{i \omega^2 L_D\beta_2/2} \FT{A}},
\end{align*}
where $L_D$ is the length of the dispersive medium. \\

>>>>

\subsection{Dispersion}
Within the laser cavity, the dispersion is dominated by the \gls{cfbg}. In comparison, the dispersion due to the fibre is negligible. The dispersive terms of \eqref{eq:nlse} give
\begin{align}
\label{eq:dispde}
	\pdiff{A}{z} = -i \frac{\beta_2}{2} \pdiff[2]{A}{T},
\end{align}
and since dispersion acts in the frequency domain it is convenient to take the Fourier transform\footnote{We use $\displaystyle \FT{f} = (2 \pi)^{-1/2} \int_\mathbb{R} f(x) \textrm{e}^{i \omega x} \df x$ as the definition of the Fourier transform.} of \eqref{eq:dispde} \cite{debnath, gradshteyn}, giving
\begin{align*}
	\pdiff{}{z}\FT{A} &= i\frac{\omega^2}{2}\beta_2 \FT{A}.
\end{align*}
The effect of dispersion is then given by the map
\begin{align*}
D(A) &= \FTi{\textrm{e}^{i \omega^2 L_D\beta_2/2} \FT{A}},
\end{align*}
where $L_D$ is the length of the dispersive medium. \\
